### 2023-10-11 main.tex
fix

\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. By varying $q$, we have a one-to-one mapping with $\bm{\tau}$. Thus, the coefficient of the above formula can be written as

@@

Therefore, we write 

@@

	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}

@@

	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}

@@

	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle

@@

We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ the configuration 

@@

This is a new configuration where the occupations $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ at sites $q_{1},\ldots,q_{i}$ are replaced with $N$'s, while the occupations on the other sites are left untouched. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation. By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain 

>>>>

\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. Thus, the coefficient of the above formula can be written as

@@

By varying $q$ and $\ell_{1},\ldots,\ell_{q}$, we have a one-to-one mapping with $\bm{\tau}$, therefore, we write 

@@

	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}\dt

@@

	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\dt

@@

	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle \dt

@@

We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ 

@@

This is a new configuration at site $x$ where, if $x\in\{q_{1},\ldots,q_{i}\}$, the occupation $\tau_{x}$ is replaced by $N$, while it is left uncaged if $x\notin \{q_{1},\ldots,q_{i}\}$. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation. By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain 
